Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-01-22 Grassmannian_cells.tex
some edits

  The \emph{universal covering quiver} $\widetilde Q$ of $Q$ has vertices $\widetilde Q_0=Q_0\times W_Q$ and arrows $\widetilde Q_1=Q_1\times W_Q$, where $(\alpha,w):\big(s(\alpha),w\big)\to\big(t(\alpha),w\alpha\big)$\sayD{Should we write $\alpha w$ here so that arrows act of the left and compose as functions?} for $\alpha\in Q_1$ and $w\in W_Q$.
  Write $G_Q:\rep\widetilde Q\to\rep Q$ for the natural functor.

@@

\begin{lemma}
  \label{le:lifts of transjectives}
  Every preprojective and preinjective representation of $Q$ can be lifted to $\hat Q$ and to $\widetilde Q$.
  \sayD{This should be upgraded to ``Any lift of a preprojective (or preinjective) for $Q$ is preprojective (or preinjective).''} 
\end{lemma}
\begin{proof}
  This statement is clear for the simple representations $S_i$, $i\in Q_0$.
  Now every preprojective or preinjective representation of $Q$ can be obtained by applying a sequence of BGP-reflections \cite{bgp} to a simple representation $S'_j$ of a quiver $Q'$ whose underlying graph is the same as the one for $Q$.
  Applying a BGP-reflection to a fixed vertex $i$ of $Q$ corresponds to applying BGP-reflections to all vertices $(i,\chi)\in\hat Q_0$, where $\chi$ runs through all $\chi\in A_Q$ (resp. to all $(i,w)\in \tilde Q_0$ with $w\in W_Q$).
  This gives the claim.
\end{proof}

@@

Write $\Sigma_1$ and $\Sigma_2$ for the BGP-reflection functors of $K(n)$ \cite{bgp}. 
We use the same symbols $\Sigma_1$, $\Sigma_2$ for the BGP-reflection functors of $K(n)^{op}$, this should not lead to any confusion. 
Then each endofunctor $\Sigma_i^2$ is naturally isomorphic to the identity map on the full subcategory $\rep_{\langle i\rangle} K(n)\subset \rep K(n)$ whose objects are those representations of $K(n)$ which do not contain the simple $S_i$ as a direct summand.
In particular, $\Sigma_i$ gives an exact equivalence of categories $\Sigma_i:\rep_{\langle i\rangle} K(n)\to\rep_{\langle i\rangle} K(n)^{op}$.
Also, following \cite{brenner-butler}, the Auslander-Reiten translation $\tau:\rep K(n)\to\rep K(n)$ may be identified with the functor $\Sigma_2\Sigma_1$.

@@

  It is easy to see that $(l,1)$ is a Schur root since all indecomposable representations with this dimension vector have trivial endomorphism ring.
  Thus the roots $d(m,r)$ are also Schur roots.
  \sayD{This can also be seen as a consequence of Corollary~\ref{cor:indecomposable truncated}, would it be better if we reorganize?}
  It follows that the set of indecomposable representations with trivial endomorphism ring form a dense open subset of $R_{d(m,r)}(K(n))$, see for example \cite[Theorem 2.2]{sch}.
  This shows the second statement.

@@

For each $m\ge2$, there is an Auslander-Reiten sequence (cf.\ \cite[Section V]{ars})
\begin{equation}
  \label{eq:AR sequence}
  0\longrightarrow P_{m-1}\stackrel{\iota_{m-1}}{\longrightarrow} P_m\otimes H_m\stackrel{ev}{\longrightarrow} P_{m+1}\longrightarrow 0,
\end{equation}
where the right-hand morphism is the natural evaluation map.

\begin{lemma}
  \label{le:injective evaluation maps}
  For any $V\in \Gr(H_m)$, $m\geq 1$, the natural evaluation map $ev_V:P_m\otimes V\to P_{m+1}$ is injective.
\end{lemma}
%%%%%%%%%%%%%%%%%%%
% needs polishing %
%%%%%%%%%%%%%%%%%%%
\begin{proof}\sayT{Maybe we can shorten the proof. I don't see a  proof which does not use reflection functors at the moment.}
  As $\Ext(P_m\otimes V,P_{m-1})=0$ and $\Hom(P_1,I_1)=0$, we obtain a commutative diagram 
  \[\xymatrix{0 \ar[r] & P_{m-1}\ar@{=}[d]\ar[r] &P_{m-1}\oplus P_m\otimes V \ar@{}[dr]|(.7){\lrcorner} \ar[r]\ar[d]_{(\iota_{m-1},\mathrm{id}_{P_m}\otimes \iota_V)} &P_{m}\otimes V \ar[r]\ar_{ev_V}[d] & 0 \ar[d]\\ 0 \ar[r] & P_{m-1}\ar[r]^{\iota_{m-1}} & P_m\otimes H_m \ar[r]^{ev} &P_{m+1} \ar[r] & I_{2-m}\ar[r]&0}\]
  in which we set $P_0=0$ and $I_l=0$ for $l\leq 0$.
  Since $\mathrm{id}_{P_1}\otimes \iota_V$ is injective, the snake lemma shows that $\ker ev_V=0$ for $m=1$ and thus $ev_V$ is injective in this case.

  In view of Remark~\ref{rem:reflection recursion}, it is enough for the case $m>1$ to show that the cokernel of $ev_V$ does not have a preinjective direct summand when $m=1$.
  Clearly the cokernel of $\mathrm{id}_{P_1}\otimes \iota_V$ is isomorphic to $P_1\otimes H_1/V$.
  Thus we obtain the following commutative diagram induced by the cokernels of the above vertical maps, note that the vertical maps below are surjective:
  \[\xymatrix{0 \ar[r]  & P_1\otimes H_1 \ar[d]\ar[r]^{ev} &P_{2}\ar[d] \ar[r] & I_{1}\ar@{=}[d]\ar[r]&0\\ 0\ar[r] & P_1\otimes H_1/V \ar[r] &K\ar[r]& I_{1}\ar[r]&0.}\]

@@

\begin{lemma}
  \label{le:unique morphisms}
  Consider $V,W\in \Gr(H_m)$, $m\ge1$.
  \begin{enumerate}
    \item There exists a morphism $P_{m+1}^W\to P_{m+1}^V$ if and only if $W\subset V$ and this morphism is unique (up to scalars) when it exists.
    \item For $W\subset V$, we have $\Ext(P_{m+1}^W,P_{m+1}^V)\cong W^*\otimes(H_m/V)$.
  \end{enumerate}
\end{lemma}
\begin{proof}
  We apply the functor $\Hom(-,P_{m+1}^V)$ to the sequence \eqref{eq:truncated preprojectives} for $W$ to get an exact sequence
  \[0\longrightarrow \Hom(P_{m+1}^W,P_{m+1}^V)\longrightarrow \Hom(P_{m+1},P_{m+1}^V)\stackrel{-\circ ev_W}{\longrightarrow} \Hom(P_m\otimes W,P_{m+1}^V)\longrightarrow \Ext(P_{m+1}^W,P_{m+1}^V)\longrightarrow 0.\]
  But the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional and thus $\Hom(P_{m+1}^W,P_{m+1}^V)$ is nonzero if and only if the right hand morphism of the above sequence is zero.
  But this occurs exactly when the image of $ev_W:P_m\otimes W\to P_{m+1}$ is contained in the kernel of $\pi_V$, i.e.\ in the image of $ev_V:P_m\otimes V\to P_{m+1}$, and this occurs if and only if $W\subset V$. 
  In this case, there are isomorphisms
  \[\Ext(P_{m+1}^W,P_{m+1}^V)\cong\Hom(P_m\otimes W,P_{m+1}^V)\cong W^*\otimes H_m/V,\]
  where the last isomorphism is immediate from Lemma~\ref{le:truncated homomorphisms}.
\end{proof}

@@

\begin{lemma}
  \label{le:basic homological properties}
  For $V\in\Gr(H_m)$, $m\ge1$, we have $\Hom(P_{m+1}^V,P_\ell)=0=\Ext(P_\ell,P_{m+1}^V)$ for all $\ell\ge1$.
\end{lemma}
\begin{proof}
  Recall that $\Hom(X,P_\ell)\ne0$ (resp. $\Ext(P_\ell,X)\ne0$) for some $\ell\ge1$ implies all indecomposable summands of $X$ are preprojectives of the form $P_r$ with $1\le r\le\ell$ (resp. $1\le r\le\ell-2$).
  However, $P_{m+1}^V$ cannot be preprojective as it is not rigid by Lemma~\ref{le:unique morphisms}.
  %Note that $\udim P_{m+1}^V <\udim P_{m+1}$, but $\udim P_r\geq \udim P_{m+1}$ if $\Hom(P_{m+1},P_r)\neq 0$.
\end{proof}

\begin{lemma}
  \label{le:reflected truncated preprojectives}
  For $V\in\Gr(H_m)$, $m\ge2$, the representation $\Sigma_1(P_{m+1}^V)^\sigma$ is also truncated preprojective.
\end{lemma}
\begin{proof}
  By Corollary~\ref{cor:indecomposable truncated} and Lemma~\ref{le:unique morphisms}, $P_{m+1}^V$ is indecomposable but not rigid.
  In particular, $P_{m+1}^V$ does not have a summand isomorphic to $S_1$.
  Thus, following Remark~\ref{rem:reflection recursion}, we may apply the functor $\Sigma_1(-)^\sigma$ to the sequence \eqref{eq:truncated preprojectives} to get the exact sequence
  \[0\longrightarrow P_{m-1}\otimes V\xrightarrow{\Sigma_1(ev_V)^\sigma} P_m\longrightarrow \Sigma_1(P_{m+1}^V)^\sigma\longrightarrow 0\]
  which gives the claim.
\end{proof}

For $V\in \Gr(H_m)$, $m\ge1$, any subspace $W\subset V$ gives rise to an exact sequence
\[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar[r]^(.6){ev} & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0},\]
where the left hand morphism above is the natural evaluation morphism coming from Lemma~\ref{le:truncated homomorphisms}.
Each such sequence has the following almost-split property for proper subrepresentations of $P_{m+1}^V$.
\begin{lemma}
  \label{le:projective subrepresentations}
  For $V\in \Gr(H_m)$, $m\ge1$, any proper subrepresentation $X\subsetneq P_{m+1}^V$ can be written as a direct sum of preprojective representations $P_r$ with $1\le r\le m$.
\end{lemma}
\begin{proof}
  We proceed by induction on $m$.
  When $m=1$, the dimension vector of $P_{m+1}^V$ is $(\codim_{H_m} V,1)$.
  In particular, it is immediate that each proper subrepresentation of $P_{m+1}^V$ is isomorphic to $P_1^k$ for some $0\le k\le\codim_{H_m} V$.

  For $m\ge2$, we observe by induction that Lemma~\ref{le:reflected truncated preprojectives} implies any subrepresentation of $P_{m+1}^V$ which has no summand isomorphic to $P_1$ must be a direct sum of preprojective representations $P_r$ with $2\le r\le m$.
  Indeed, each of these is obtained from a subrepresentation of $\Sigma_1(P_{m+1}^V)^\sigma$ by applying the functor $\Sigma_2(-)^\sigma$ and the claim follows from the recursions in Remark~\ref{rem:reflection recursion} for preprojective representations.
\end{proof}
\begin{corollary}
  Consider $V,W\in \Gr(H_m)$, $m\ge1$, with $W\subset V$.
  Given any proper subrepresentation $X\subsetneq P_{m+1}^V$ and any subrepresentation $Z\subset P_m\otimes(V/W)$, there is a subrepresentation of $P_{m+1}^W$ isomorphic to $Z\oplus X$ which fits into a commutative diagram
  \[\xymatrix{0 \ar[r] & Z \ar[d]\ar[r] & Z\oplus X \ar[r]\ar[d] & X \ar[d]\ar[r] & 0 \\
    0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
\end{corollary}
\begin{proof}
  Observe that $\Ext(P_r,P_m)=0$ for $1\le r\le m$ and, since $X$ is a direct sum of preprojectives, the upper pullback sequence
  \[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar@{=}[d]\ar[r] & Y \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & X \ar[d]\ar[r] & 0 \\
    0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
  must split.
  The claim for arbitrary subrepresentations $Z\subset P_m\otimes(V/W)$ is an immediate consequence of this splitting.
\end{proof}

@@

\begin{lemma}
  \label{le:truncated extensions}
  For $V\in \Gr(H_m)$, $m\ge1$, we have $\Ext(P_{m+1}^V,P_m)\cong V^*$, where each nontrivial extension naturally corresponds to a codimension 1 subspace $U\subset V$. 
  More precisely, each element of $\Ext(P_{m+1}^V,P_m)$ corresponds to an exact sequence
  \[\xymatrix{0 \ar[r] & P_m \ar[r] & P_{m+1}^U \ar[r] & P_{m+1}^V \ar[r] & 0},\]
where $U\subset V$ satisfies $\dim(V/U)=1$.
\end{lemma}
\begin{proof}
  Consider a nonzero map $\varphi\in V^*$ and set $U=\ker\varphi\subset V$.
  There is a natural isomorphism $V^*\cong\Hom(P_m\otimes V,P_m)$ which takes $\varphi$ to $id\overline{\otimes}\varphi$.
  This gives rise to the following commutative diagram:
  \[\xymatrix{ & 0 \ar[d] & 0 \ar[d] & & \\
    & P_m\otimes U \ar@{=}[r]\ar[d] & P_m\otimes U \ar[d] & & \\
    0 \ar[r] & P_m\otimes V \ar[d]^{id\overline{\otimes}\varphi}\ar[r]\ar@{}[dr]|(.7){\lrcorner}\ar@{}[dr]|(.3){\ulcorner} & P_{m+1} \ar[r]\ar[d] & P_{m+1}^V \ar[r]\ar@{=}[d] & 0\\
    0 \ar[r] & P_m \ar[r]\ar[d] & P_{m+1}^U \ar[r]\ar[d] & P_{m+1}^V \ar[r] & 0\\
   & 0 & 0 & & }\]
  But observe that we may apply the functor $\Hom(-,P_m)$ to the sequence \eqref{eq:truncated preprojectives} to get the isomorphism 
  \[\Ext(P_{m+1}^V,P_m)\cong\Hom(P_m\otimes V,P_m)\cong V^*.\]
  Under this isomorphism, the functional $\varphi$ corresponds to the lower pushout sequence in the above diagram.
\end{proof}

@@

\sayD{The next result needs some serious clean-up, can they be proven for $K(n)$ without passing to the universal cover?}
\begin{lemma}
  For $V\in \Gr(H_m)$, $m\ge1$, a subrepresentation $X\subset P_m$ fits into a commutative diagram
  \[\xymatrix{0 \ar[r] & X \ar[d]\ar[r]\ar@{}[dr]|(.3){\ulcorner} & Y \ar[d]\ar[r] & P_{m+1}^V \ar@{=}[d]\ar[r] & 0 \\
    0 \ar[r] & P_m\otimes(V/U) \ar[r] & P_{m+1}^U \ar[r] & P_{m+1}^V \ar[r] & 0}\]
  with $\dim(V/U)=1$ if and only if the lower pushout sequence below splits: 
  \[\xymatrix{ 0\ar[r]& P_m\otimes(V/U) \ar[r] \ar[d]\ar@{}[dr]|(.3){\ulcorner} & P_{m+1}^U \ar[r]\ar[d] & P_{m+1}^V \ar@{=}[d]\ar[r] & 0\\
  0 \ar[r] & P_m\otimes(V/U)/X \ar[r] & Z \ar[r] & P_{m+1}^V \ar[r] & 0}.\]
  This occurs (?) if and only if the composed morphism
  \[\xymatrix{X \ar[r] & P_m \ar[r] & P_m^{\bar{V}} \ar[r] & P_{m-1}^{\bar{\bar{V}}}}\]
  is nonzero.
\end{lemma}
\begin{proof}
  For a proper subrepresentation $X\subsetneq P_m$ we have the following commutative diagram
  \[\tag{$\dagger$}\xymatrix{ & 0 \ar[r]\ar[d] & \Hom(P_{m+1}^U,P_m/X) \ar[d]\\
    0 \ar[r]\ar[d] & \Hom(P_m,P_m) \ar[r]\ar[d] & \Hom(P_m,P_m/X) \ar[d]\\
    \Ext(P_{m+1}^V,X) \ar[r] & \Ext(P_{m+1}^V,P_m) \ar[r] & \Ext(P_{m+1}^V,P_m/X)}\]
  From the bottom row of the diagram ($\dagger$), we see that there is a pushout diagram
  \[\xymatrix{0 \ar[r] & X \ar[d]\ar[r]\ar@{}[dr]|(.3){\ulcorner} & Y \ar[d]\ar[r] & P_{m+1}^V \ar@{=}[d]\ar[r] & 0 \\
    0 \ar[r] & P_m \ar[r] & P_{m+1}^U \ar[r] & P_{m+1}^V \ar[r] & 0}\]
  if and only if the lower pushout sequence below splits: 
  \[\xymatrix{ 0\ar[r]& P_m \ar[r]^{\epsilon}\ar[d]_{\rho}\ar@{}[dr]|(.3){\ulcorner} & P_{m+1}^U \ar[r]\ar[d] & P_{m+1}^V \ar@{=}[d]\ar[r] & 0\\
  0 \ar[r] & P_m/X \ar[r] & Z \ar[r] & P_{m+1}^V \ar[r] & 0}.\]
  The right hand vertical sequence of the diagram ($\dagger$) then shows that this occurs if and only if the map $\rho:P_m\to P_m/X$ factors through the map $\epsilon:P_m\to P_{m+1}^U$.

@@

As the lifts of all (truncated) preprojectives are exceptional as representations of $\widetilde{K(n)}$, they are uniquely determined by their dimension vector.
We use this fact and do not state the particular maps defining the lifts.
In this example, we just state the support of the representation including those dimensions which are not one.
We call it the quiver of the representations.

>>>>

  The \emph{universal covering quiver} $\widetilde Q$ of $Q$ has vertices $\widetilde Q_0=Q_0\times W_Q$ and arrows $\widetilde Q_1=Q_1\times W_Q$, where $(\alpha,w):\big(s(\alpha),w\big)\to\big(t(\alpha),w\alpha\big)$ for $\alpha\in Q_1$ and $w\in W_Q$.
  Write $G_Q:\rep\widetilde Q\to\rep Q$ for the natural functor.

@@

\begin{lemma}
  Every preprojective and preinjective representation of $Q$ can be lifted to $\hat Q$ and $\widetilde Q$.
\end{lemma}
\begin{proof}
  This statement is clear for the simple representations $S_i$, $i\in Q_0$.
  Now every preprojective or preinjective representation of $Q$ can be obtained by applying a sequence of BGP-reflections \cite{bgp} to a simple representation $S'_j$ of a quiver $Q'$ whose underlying graph is the same as the one for $Q$.
  Applying a BGP-reflection to a fixed vertex $i$ of $Q$ corresponds to applying BGP-reflections to all vertices $(i,\chi)\in\hat Q_0$, where $\chi$ runs through all $\chi\in A_Q$ (resp. to all $(i,w)\in \tilde Q_0$ with $w\in W_Q$).
  This gives the claim.
\end{proof}

@@

Write $\Sigma_1$ and $\Sigma_2$ for the BGP-reflection functors of $K(n)$ \cite{bgp}. 
We use the same symbols $\Sigma_1$, $\Sigma_2$ for the BGP-reflection functors of $K(n)^{op}$, this should not lead to any confusion. 
Then the endofunctors $\Sigma_1^2$ and $\Sigma_2^2$ are each naturally isomorphic to the identity maps on the full subcategories $\rep_{\langle 1\rangle} K(n),\rep_{\langle 2\rangle} K(n)\subset \rep K(n)$, where the objects of $\rep_{\langle i\rangle} K(n)$ are those representations of $K(n)$ which do not contain the simple $S_i$ as a direct summand.
Also, following \cite{brenner-butler}, the Auslander-Reiten translation $\tau:\rep K(n)\to\rep K(n)$ may be identified with the functor $\Sigma_2\Sigma_1$.

@@

  It is easy to see that $(l,1)$ is a Schur root since all indecomposable representations with this dimension vector have trivial endomorphism ring.
  Thus the roots $d(m,r)$ are also Schur roots.
  \sayD{This can also be seen as a consequence of Corollary~\ref{cor:indecomposable truncated}, would it be better if we reorganize?}
  It follows that the set of indecomposable representations with trivial endomorphism ring form a dense open subset of $R_{d(m,r)}(K(n))$, see for example \cite{sch}.
  This shows the second statement.

@@

For each $m\ge2$, there is an Auslander-Reiten sequence \cite[Section V]{ars}
\begin{equation}
  \label{eq:AR sequence}
  0\longrightarrow P_{m-1}\stackrel{\iota_{m-1}}{\longrightarrow} P_m\otimes H_m\stackrel{ev}{\longrightarrow} P_{m+1}\longrightarrow 0,
\end{equation}
where the right-hand morphism is the natural evaluation map.

\begin{lemma}
  \label{le:injective evaluation maps}
Let $m\geq 1$.  For any $V\in \Gr(H_m)$, the natural evaluation map $ev_V:P_m\otimes V\to P_{m+1}$ is injective.
\end{lemma}
%%%%%%%%%%%%%%%%%%%
% needs polishing %
%%%%%%%%%%%%%%%%%%%
\begin{proof}\sayT{Maybe we can shorten the proof. I don't see a  proof which does not use reflection functors at the moment.}
  As $\Ext(P_m\otimes V,P_{m-1})=0$ and $\Hom(P_1,I_1)=0$, we obtain a commutative diagram 
  \[\xymatrix{0 \ar[r] & P_{m-1}\ar[r]^{\iota_{m-1}} & P_m\otimes H_m \ar[r]^{ev} &P_{m+1} \ar[r] & I_{2-m}\ar[r]&0\\0 \ar[r] & P_{m-1}\ar@{=}[u]\ar[r] &P_{m-1}\oplus P_m\otimes V \ar@{}[ur]|(.7){\urcorner} \ar[r]\ar[u]^{(\iota_{m-1},\mathrm{id}_{P_m}\otimes \iota_V)} &P_{m}\otimes V \ar[r]\ar_{ev_V}[u] & 0 \ar[u]}\]
  in which we set $P_0=0$ and $I_l=0$ for $l\leq 0$.
  Since $\mathrm{id}_{P_1}\otimes \iota_V$ is injective, the snake lemma shows that $\ker ev_V=0$ for $m=1$ and thus $ev_V$ is injective in this case.

  In view of Remark~\ref{rem:reflection recursion}, it is enough for the case $m>1$ to show that the cokernel of $ev_V$ does not have a preinjective direct summand when $m=1$.
  Clearly the cokernel of $\mathrm{id}_{P_1}\otimes \iota_V$ is isomorphic to $P_1\otimes H_1/V$.
  Thus we obtain the following commutative diagram induced by the cokernels of the above vertical maps, note that the vertical maps below are surjective:
  \[\xymatrix{0\ar[r] & P_1\otimes H_1/V \ar[r] &K\ar[r]& I_{1}\ar[r]&0\\0 \ar[r]  & P_1\otimes H_1 \ar[u]\ar[r]^{ev} &P_{2}\ar[u] \ar[r] & I_{1}\ar@{=}[u]\ar[r]&0.}\]

@@

\begin{lemma}
  \label{le:unique morphisms}
  Consider $V,W\in \Gr(H_m)$, $m\ge1$.
  \begin{enumerate}
    \item There exists a morphism $P_{m+1}^W\to P_{m+1}^V$ if and only if $W\subset V$ and this morphism is unique (up to scalars) when it exists.
    \item For $W\subset V$, we have $\Ext(P_{m+1}^W,P_{m+1}^V)\cong W^*\otimes(H_m/V)$.
  \end{enumerate}
\end{lemma}
\begin{proof}
  We apply the functor $\Hom(-,P_{m+1}^V)$ to the sequence \eqref{eq:truncated preprojectives} for $W$ to get an exact sequence
  \[0\longrightarrow \Hom(P_{m+1}^W,P_{m+1}^V)\longrightarrow \Hom(P_{m+1},P_{m+1}^V)\stackrel{-\circ ev_W}{\longrightarrow} \Hom(P_m\otimes W,P_{m+1}^V)\longrightarrow \Ext(P_{m+1}^W,P_{m+1}^V)\longrightarrow 0.\]
  But the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional and thus $\Hom(P_{m+1}^W,P_{m+1}^V)$ is nonzero if and only if the right hand morphism of the above sequence is zero.
  But this occurs exactly when the image of $ev_W:P_m\otimes W\to P_{m+1}$ is contained in the kernel of $\pi_V$, i.e.\ in the image of $ev_V:P_m\otimes V\to P_{m+1}$, and this occurs if and only if $W\subset V$. 
  In this case, there is an isomorphism 
  \[\Ext(P_{m+1}^W,P_{m+1}^V)\cong\Hom(P_m\otimes W,P_{m+1}^V)\cong W^*\otimes H_m/V,\]
  where the last isomorphism is immediate from Lemma~\ref{le:truncated homomorphisms}.
\end{proof}

@@

\begin{lemma}
  \label{le:basic homological properties}
  For $V\in \Gr(H_m)$, $m\ge1$, we have $\Hom(P_{m+1}^V,P_\ell)=0=\Ext(P_\ell,P_{m+1}^V)$ for all $\ell\ge1$.
\end{lemma}
\begin{proof}
  Recall that $\Hom(X,P_\ell)\ne0$ (resp. $\Ext(P_\ell,X)\ne0$) for some $\ell\ge1$ implies all indecomposable summands of $X$ are preprojectives of the form $P_r$ with $1\le r\le\ell$ (resp. $1\le r\le\ell-2$).
  However, $P_{m+1}^V$ cannot be preprojective as it is not rigid by Lemma~\ref{le:unique morphisms}.
  %Note that $\udim P_{m+1}^V <\udim P_{m+1}$, but $\udim P_r\geq \udim P_{m+1}$ if $\Hom(P_{m+1},P_r)\neq 0$.
\end{proof}

@@

\begin{lemma}
  \label{le:truncated extensions}
  For $V\in \Gr(H_m)$, $m\ge1$, we have $\Ext(P_{m+1}^V,P_m)\cong V^*$, where each nontrivial extension naturally corresponds to a codimension 1 subspace $U\subset V$. 
  More precisely, each element of $\Ext(P_{m+1}^V,P_m)$ corresponds to an exact sequence
  \[\xymatrix{0 \ar[r] & P_m \ar[r] & P_{m+1}^U \ar[r] & P_{m+1}^V \ar[r] & 0},\]
where $U\subset V$ satisfies $\dim(V/U)=1$.
\end{lemma}
\begin{proof}
  Consider a nonzero map $\varphi\in V^*$ and set $U=\ker\varphi\subset V$.
  There is a natural isomorphism $V^*\cong\Hom(P_m\otimes V,P_m)$ which takes $\varphi$ to $id\overline{\otimes}\varphi$.
  This gives rise to the following commutative diagram:
  \[\xymatrix{ & 0 \ar[d] & 0 \ar[d] & & \\
    & P_m\otimes U \ar@{=}[r]\ar[d] & P_m\otimes U \ar[d] & & \\
    0 \ar[r] & P_m\otimes V \ar[d]^{id\overline{\otimes}\varphi}\ar[r]\ar@{}[dr]|(.7){\lrcorner}\ar@{}[dr]|(.3){\ulcorner} & P_{m+1} \ar[r]\ar[d] & P_{m+1}^V \ar[r]\ar@{=}[d] & 0\\
    0 \ar[r] & P_m \ar[r]\ar[d] & P_{m+1}^U \ar[r]\ar[d] & P_{m+1}^V \ar[r] & 0\\
   & 0 & 0 & & }\]
  By Lemma~\ref{le:basic homological properties}, we may apply the functor $\Hom(-,P_m)$ to the sequence \eqref{eq:truncated preprojectives} to get the isomorphism 
  \[\Ext(P_{m+1}^V,P_m)\cong\Hom(P_m\otimes V,P_m)\cong V^*.\]
  Under this isomorphism, the functional $\varphi$ corresponds to the lower pushout sequence in the above diagram.
\end{proof}

@@

For $V\in \Gr(H_m)$, $m\ge1$, any subspace $W\subset V$ gives rise to an exact sequence
\[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar[r]^(.6){ev} & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0},\]
where the left hand morphism above is the natural evaluation morphism coming from Lemma~\ref{le:truncated homomorphisms}.
Each such sequence has the following almost-split property for proper subrepresentations of $P_{m+1}^V$.
\sayD{The next results need some serious clean-up, can they be proven for $K(n)$ without passing to the universal cover?}
\begin{lemma}
  For $V\in \Gr(H_m)$, $m\ge1$, any proper subrepresentation $X\subsetneq P_{m+1}^V$ can be written as a direct sum of preprojective representations $P_r$ with $1\le r\le m$.
  Moreover, the upper pullback sequence
  \[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar@{=}[d]\ar[r] & Y \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & X \ar[d]\ar[r] & 0 \\
    0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
  splits for every proper subspace $W\subsetneq V$.
\end{lemma}
\begin{proof}
  We proceed by simultaneous induction on $m$ and $\codim_{H_m} V$.

  When $m=1$, the dimension vector of $P_{m+1}^V$ is $(\codim_{H_m} V,1)$.
  In particular, it is immediate that each proper subrepresentation of $P_{m+1}^V$ is isomorphic to $P_1^k$ for some $0\le k\le l$ which gives both claims in this case.

  By Corollary~\ref{cor:truncated preprojective isomorphism}, the first claim for $m\ge2$ and $\codim_{H_m} V = 1$ follows from the first claim for $m-1$.

  Now we show that the first claim implies the second.
  Consider $W\subsetneq V$ and suppose the first claim holds for $P_{m+1}^V$.
  Observe that $\Ext(P_r,P_m)=0$ for $1\le r\le m$ and so the upper pullback sequence above will split giving the second claim.

  We proceed by induction on $\codim_V W$.  
  When $\codim_V W=1$, we have an exact sequence
  \[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\] 
  with both morphisms irreducible by Lemma~\ref{le:irreducible morphisms} and the claim immediately follows.

  Suppose $W\subsetneq V$ with $\codim_V W>1$ and choose an intermediate subspace $W\subsetneq T\subsetneq V$.
  Given $X\subsetneq P_{m+1}^V$, we have the pullback diagram
  \[\xymatrix{ Y \ar[d]\ar[r]\ar@{}[dr]|(.7){\lrcorner} & Y' \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & X \ar[d]\\
  P_{m+1}^W \ar[r] & P_{m+1}^T \ar[r] & P_{m+1}^V}\]
  in which all horizontal morphisms of the upper row are split epimorphisms by induction.
  The result now follows since the outer square is also a pullback.
\end{proof}
\begin{corollary}
  Consider $V,W\in \Gr(H_m)$, $m\ge1$, with $W\subset V$.
  Given any proper subrepresentation $X\subsetneq P_{m+1}^V$ and any subrepresentation $Z\subset P_m\otimes(V/W)$, there is a subrepresentation of $P_{m+1}^W$ isomorphic to $Z\oplus X$ which fits into a commutative diagram
  \[\xymatrix{0 \ar[r] & Z \ar[d]\ar[r] & Z\oplus X \ar[r]\ar[d] & X \ar[d]\ar[r] & 0 \\
    0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
\end{corollary}

\begin{lemma}
  For $V\in \Gr(H_m)$, $m\ge1$, a subrepresentation $X\subset P_m$ fits into a commutative diagram
  \[\xymatrix{0 \ar[r] & X \ar[d]\ar[r]\ar@{}[dr]|(.3){\ulcorner} & Y \ar[d]\ar[r] & P_{m+1}^V \ar@{=}[d]\ar[r] & 0 \\
    0 \ar[r] & P_m\otimes(V/U) \ar[r] & P_{m+1}^U \ar[r] & P_{m+1}^V \ar[r] & 0}\]
  with $\dim(V/U)=1$ if and only if the lower pushout sequence below splits: 
  \[\xymatrix{ 0\ar[r]& P_m\otimes(V/U) \ar[r] \ar[d]\ar@{}[dr]|(.3){\ulcorner} & P_{m+1}^U \ar[r]\ar[d] & P_{m+1}^V \ar@{=}[d]\ar[r] & 0\\
  0 \ar[r] & P_m\otimes(V/U)/X \ar[r] & Z \ar[r] & P_{m+1}^V \ar[r] & 0}.\]
  This occurs (?) if and only if the composed morphism
  \[\xymatrix{X \ar[r] & P_m \ar[r] & P_m^{\bar{V}} \ar[r] & P_{m-1}^{\bar{\bar{V}}}}\]
  is nonzero.
\end{lemma}
\begin{proof}
  For a proper subrepresentation $X\subsetneq P_m$ we have the following commutative diagram
  \[\tag{$\dagger$}\xymatrix{ & 0 \ar[r]\ar[d] & \Hom(P_{m+1}^U,P_m/X) \ar[d]\\
    0 \ar[r]\ar[d] & \Hom(P_m,P_m) \ar[r]\ar[d] & \Hom(P_m,P_m/X) \ar[d]\\
    \Ext(P_{m+1}^V,X) \ar[r] & \Ext(P_{m+1}^V,P_m) \ar[r] & \Ext(P_{m+1}^V,P_m/X)}\]
  From the bottom row of the diagram ($\dagger$), we see that there is a pushout diagram
  \[\xymatrix{0 \ar[r] & X \ar[d]\ar[r]\ar@{}[dr]|(.3){\ulcorner} & Y \ar[d]\ar[r] & P_{m+1}^V \ar@{=}[d]\ar[r] & 0 \\
    0 \ar[r] & P_m \ar[r] & P_{m+1}^U \ar[r] & P_{m+1}^V \ar[r] & 0}\]
  if and only if the lower pushout sequence below splits: 
  \[\xymatrix{ 0\ar[r]& P_m \ar[r]^{\epsilon}\ar[d]_{\rho}\ar@{}[dr]|(.3){\ulcorner} & P_{m+1}^U \ar[r]\ar[d] & P_{m+1}^V \ar@{=}[d]\ar[r] & 0\\
  0 \ar[r] & P_m/X \ar[r] & Z \ar[r] & P_{m+1}^V \ar[r] & 0}.\]
  The right hand vertical sequence of the diagram ($\dagger$) then shows that this occurs if and only if the map $\rho:P_m\to P_m/X$ factors through the map $\epsilon:P_m\to P_{m+1}^U$.

@@

As the lifts of all (truncated) preprojectives are exceptional as representations of $\widetilde{K(n)}$, they are uniquely determined by its dimension vector. We use this fact and do not state the particular maps defining the lifts. In this example, we just state the support of the representation including those dimensions which are not one. We call it the quiver of the representations.

The representation $\tilde P_2$ is defined by the following quiver:
